



INTRODUCTION
====================

TWO TYPES OF DB's
	- RELATIONAL DATABASES 
	- NON RELATIONAL DATABASES
	
MySQL is a widely used relational database management system (RDBMS).

MySQL is free and open-source.

MySQL is ideal for both small and large applications.


What is MySQL?
==========================
MySQL is a relational database management system
MySQL is open-source
MySQL is free
MySQL is ideal for both small and large applications
MySQL is very fast, reliable, scalable, and easy to use
MySQL is cross-platform (windows , unix/linux, macos)
MySQL is compliant with the ANSI SQL standard
MySQL was first released in 1995
MySQL is developed, distributed, and supported by Oracle Corporation
MySQL is named after co-founder Monty Widenius's daughter: My


Show Data On Your Web Site
======================================
To build a web site that shows data from a database, you will need:

An RDBMS database program (like MySQL)
A server-side scripting language, like PYTHON , JAVA
To use SQL to get the data you want
To use HTML / CSS to style the page

user ------->- website (html,css,js) FRONTEND -------> BACKEND(java/python/ruby) ------> DB server.

What is RDBMS?
=============================
RDBMS stands for Relational Database Management System.

RDBMS is a program used to maintain a relational database.

RDBMS is the basis for all modern database systems such as MySQL, Microsoft SQL Server, Oracle, and Microsoft Access.

RDBMS uses SQL queries to access the data in the database.


price > 50 ---- SQL(query) ---- DBSERVER(DATABASE) 

SELECT * from Cart where price > 50;


TERMINOLOGIES 
======================
SERVER
DATABASE
SCHEMA 
TABLE 
ROW
COLUMN
PRIMARYKEY 


how to install? (10mins)
------------------------ 	
https://www.youtube.com/watch?v=Rxp3T5GKlR4

- SERVER
- WORKBENCH 
- SHELL 

PORT : 3306. 

how to check 
====================

open CMD :
	type : mysql --version

difference SQL VS NO SQL 
==========================

https://www.geeksforgeeks.org/difference-between-sql-and-nosql/



POPULAR COMMANDS
=======================
mysql 
SELECT - extracts data from a database
UPDATE - updates data in a database
DELETE - deletes data from a database
INSERT INTO - inserts new data into a database
CREATE DATABASE - creates a new database
ALTER DATABASE - modifies a database
CREATE TABLE - creates a new table
ALTER TABLE - modifies a table
DROP TABLE - deletes a table
CREATE INDEX - creates an index (search key)
DROP INDEX - deletes an index


EX:
	DATABASE : FOOD 
	TABLES : items 
	
CREATE TABLE items (
    ID int,
    name varchar(255),
    price int,
    review varchar(255)
);

INSERT INTO items (ID, name, price,review)
VALUES (2, "chicken fried rice", 55, "ok");

INSERT INTO items (ID, name, price,review)
VALUES (6, "lemon juice", 45, "sweety");


UPDATE items
SET price = 65, name = "chicken fried rice"
WHERE ID =2;



DELETE FROM items WHERE ID =2;
	
	
CRUD operations 
=======================
CREATE READ UPDATE DELETE...


APPLICATION (python) INTERACT with DB(MYSQL)
====================================


